Casual Bandits

### 2016-01-29 causal-bandit/icml-2015/setup.tex
Note on ordering of act-observe-reward

@@

We now consider a class of a causal bandit problems which we call \emph{parallel bandits}.
It is simple enough to admit a thorough analysis but rich enough to model the type of problem discussed in \S\ref{sec:intro}, including the farming example.

>>>>

Although we will focus on the intervene-observe-reward ordering of events within each round, others are also possible. 
If the non-intervened variables are observed before an intervention is selected our framework reduces to stochastic contextual bandits, which are already well understood~\citep{Agarwal2014}. 
Even if no observations are made during the rounds, the causal model may still allow offline pruning of the set of allowable interventions thereby reducing the complexity.

@@

We now consider a class of a causal bandit problems which we call \emph{parallel bandits}.
It is simple enough to admit a thorough analysis but rich enough to model the type of problem discussed in \S\ref{sec:intro}, including the farming example. It also suffices to witness the regret gap between algorithms that make use of causal models and those which do not.
